A comparison of design-based and model-based approaches for finite population spatial data -- Supporting Information.

### 2021-12-22 inst/manuscript/supporting.tex
update simulations to include standard errors in summaries
more minor updates to incorporate mean standard error addition

Recall the four design-analysis combinations and the parameter
configurations, summarized in Table \ref{tab:designanalysis} and
\ref{tab:parmtab}, respectively.

\begin{table}[ht]
\centering
\begin{tabular}{r|ll}
  \hline
 & Design & Model \\ 
  \hline
IRS & IRS-Design & IRS-Model \\ 
  GRTS & GRTS-Design & GRTS-Model \\ 
   \hline
\end{tabular}
\caption{\label{tab:designanalysis} Types of Sampling Design and Analysis combinations considered in the simulation study. The rows give the two types of sampling designs while the columns give the two types of analyses.} 
\end{table}

\begin{table}[ht]
\centering
\begin{tabular}{r|lll}
   \hline
Sample Size (n) & 50 & 100 & 200 \\ 
  Layout & Random & Gridded & - \\ 
  Proportion of Dependent Error & 0 & 0.5 & 0.9 \\ 
  Response Type & Normal & Lognormal & - \\ 
   \hline
\end{tabular}
\caption{\label{tab:parmtab} Simulation parameters. Total variability for all scenarios was 2.} 
\end{table}

Next we present a summary table for each of the 36 simulation scenarios.

@@

\scalebox{0.85}{
\begin{tabular}{lllllrrr}

@@

Approach & Layout & Response & DE Prop & n & Bias & rMS(P)E & Coverage \\ 

@@

IRS-Design & Gridded & Normal & 0 & 50 & -0.0023 & 0.1968 & 0.9440 \\ 
  IRS-Model & Gridded & Normal & 0 & 50 & -0.0029 & 0.1988 & 0.9400 \\ 
  GRTS-Design & Gridded & Normal & 0 & 50 & -0.0011 & 0.1946 & 0.9110 \\ 
  GRTS-Model & Gridded & Normal & 0 & 50 & -0.0006 & 0.1949 & 0.9300 \\ 

@@

\caption{Approach, layout (Layout), response type (Response) roportion of dependent error (DE Prop), sample size (n), mean (prediction) bias (Bias), root-mean-squared-(prediction) error (rMS(P)E), and 95\% interval coverage (Coverage) for a simulation scenario.} 

@@

IRS-Design & Gridded & Lognormal & 0 & 50 & -0.0036 & 0.2007 & 0.9080 \\ 
  IRS-Model & Gridded & Lognormal & 0 & 50 & -0.0094 & 0.2071 & 0.9045 \\ 
  GRTS-Design & Gridded & Lognormal & 0 & 50 & -0.0007 & 0.1962 & 0.8690 \\ 
  GRTS-Model & Gridded & Lognormal & 0 & 50 & -0.0022 & 0.1969 & 0.8945 \\ 

@@

\caption{Approach, layout (Layout), response type (Response) roportion of dependent error (DE Prop), sample size (n), mean (prediction) bias (Bias), root-mean-squared-(prediction) error (rMS(P)E), and 95\% interval coverage (Coverage) for a simulation scenario.} 

@@

IRS-Design & Random & Normal & 0 & 50 & 0.0019 & 0.1861 & 0.9505 \\ 
  IRS-Model & Random & Normal & 0 & 50 & 0.0014 & 0.1892 & 0.9445 \\ 
  GRTS-Design & Random & Normal & 0 & 50 & -0.0040 & 0.1955 & 0.9090 \\ 
  GRTS-Model & Random & Normal & 0 & 50 & -0.0040 & 0.1965 & 0.9315 \\ 

@@

\caption{Approach, layout (Layout), response type (Response) roportion of dependent error (DE Prop), sample size (n), mean (prediction) bias (Bias), root-mean-squared-(prediction) error (rMS(P)E), and 95\% interval coverage (Coverage) for a simulation scenario.} 

@@

IRS-Design & Random & Lognormal & 0 & 50 & 0.0032 & 0.1843 & 0.9205 \\ 
  IRS-Model & Random & Lognormal & 0 & 50 & -0.0039 & 0.1945 & 0.9105 \\ 
  GRTS-Design & Random & Lognormal & 0 & 50 & -0.0056 & 0.1944 & 0.8870 \\ 
  GRTS-Model & Random & Lognormal & 0 & 50 & -0.0078 & 0.1967 & 0.9075 \\ 

@@

\caption{Approach, layout (Layout), response type (Response) roportion of dependent error (DE Prop), sample size (n), mean (prediction) bias (Bias), root-mean-squared-(prediction) error (rMS(P)E), and 95\% interval coverage (Coverage) for a simulation scenario.} 

@@

IRS-Design & Gridded & Normal & 0.5 & 50 & 0.0025 & 0.1762 & 0.9470 \\ 
  IRS-Model & Gridded & Normal & 0.5 & 50 & 0.0007 & 0.1655 & 0.9305 \\ 
  GRTS-Design & Gridded & Normal & 0.5 & 50 & 0.0004 & 0.1524 & 0.9115 \\ 
  GRTS-Model & Gridded & Normal & 0.5 & 50 & -0.0003 & 0.1499 & 0.9320 \\ 

@@

\caption{Approach, layout (Layout), response type (Response) roportion of dependent error (DE Prop), sample size (n), mean (prediction) bias (Bias), root-mean-squared-(prediction) error (rMS(P)E), and 95\% interval coverage (Coverage) for a simulation scenario.} 

@@

IRS-Design & Gridded & Lognormal & 0.5 & 50 & 0.0004 & 0.1863 & 0.9140 \\ 
  IRS-Model & Gridded & Lognormal & 0.5 & 50 & -0.0076 & 0.1834 & 0.9035 \\ 
  GRTS-Design & Gridded & Lognormal & 0.5 & 50 & 0.0016 & 0.1612 & 0.8810 \\ 
  GRTS-Model & Gridded & Lognormal & 0.5 & 50 & -0.0017 & 0.1606 & 0.8940 \\ 

@@

\caption{Approach, layout (Layout), response type (Response) roportion of dependent error (DE Prop), sample size (n), mean (prediction) bias (Bias), root-mean-squared-(prediction) error (rMS(P)E), and 95\% interval coverage (Coverage) for a simulation scenario.} 

@@

IRS-Design & Random & Normal & 0.5 & 50 & 0.0037 & 0.1657 & 0.9590 \\ 
  IRS-Model & Random & Normal & 0.5 & 50 & 0.0027 & 0.1546 & 0.9495 \\ 
  GRTS-Design & Random & Normal & 0.5 & 50 & -0.0034 & 0.1511 & 0.9170 \\ 
  GRTS-Model & Random & Normal & 0.5 & 50 & -0.0037 & 0.1504 & 0.9305 \\ 

@@

\caption{Approach, layout (Layout), response type (Response) roportion of dependent error (DE Prop), sample size (n), mean (prediction) bias (Bias), root-mean-squared-(prediction) error (rMS(P)E), and 95\% interval coverage (Coverage) for a simulation scenario.} 

@@

IRS-Design & Random & Lognormal & 0.5 & 50 & 0.0023 & 0.1637 & 0.9245 \\ 
  IRS-Model & Random & Lognormal & 0.5 & 50 & -0.0055 & 0.1622 & 0.9125 \\ 
  GRTS-Design & Random & Lognormal & 0.5 & 50 & -0.0057 & 0.1570 & 0.9000 \\ 
  GRTS-Model & Random & Lognormal & 0.5 & 50 & -0.0079 & 0.1567 & 0.9100 \\ 

@@

\caption{Approach, layout (Layout), response type (Response) roportion of dependent error (DE Prop), sample size (n), mean (prediction) bias (Bias), root-mean-squared-(prediction) error (rMS(P)E), and 95\% interval coverage (Coverage) for a simulation scenario.} 

@@

IRS-Design & Gridded & Normal & 0.9 & 50 & 0.0053 & 0.1579 & 0.9470 \\ 
  IRS-Model & Gridded & Normal & 0.9 & 50 & 0.0026 & 0.1165 & 0.9315 \\ 
  GRTS-Design & Gridded & Normal & 0.9 & 50 & 0.0013 & 0.1074 & 0.9220 \\ 
  GRTS-Model & Gridded & Normal & 0.9 & 50 & -0.0007 & 0.0949 & 0.9430 \\ 

@@

\caption{Approach, layout (Layout), response type (Response) roportion of dependent error (DE Prop), sample size (n), mean (prediction) bias (Bias), root-mean-squared-(prediction) error (rMS(P)E), and 95\% interval coverage (Coverage) for a simulation scenario.} 

@@

IRS-Design & Gridded & Lognormal & 0.9 & 50 & 0.0031 & 0.1731 & 0.9220 \\ 
  IRS-Model & Gridded & Lognormal & 0.9 & 50 & -0.0020 & 0.1325 & 0.9135 \\ 
  GRTS-Design & Gridded & Lognormal & 0.9 & 50 & 0.0031 & 0.1183 & 0.9065 \\ 
  GRTS-Model & Gridded & Lognormal & 0.9 & 50 & -0.0002 & 0.1090 & 0.9120 \\ 

@@

\caption{Approach, layout (Layout), response type (Response) roportion of dependent error (DE Prop), sample size (n), mean (prediction) bias (Bias), root-mean-squared-(prediction) error (rMS(P)E), and 95\% interval coverage (Coverage) for a simulation scenario.} 

@@

IRS-Design & Random & Normal & 0.9 & 50 & 0.0062 & 0.1520 & 0.9525 \\ 
  IRS-Model & Random & Normal & 0.9 & 50 & 0.0037 & 0.1074 & 0.9525 \\ 
  GRTS-Design & Random & Normal & 0.9 & 50 & -0.0029 & 0.1038 & 0.9340 \\ 
  GRTS-Model & Random & Normal & 0.9 & 50 & -0.0027 & 0.0940 & 0.9360 \\ 

@@

\caption{Approach, layout (Layout), response type (Response) roportion of dependent error (DE Prop), sample size (n), mean (prediction) bias (Bias), root-mean-squared-(prediction) error (rMS(P)E), and 95\% interval coverage (Coverage) for a simulation scenario.} 

@@

IRS-Design & Random & Lognormal & 0.9 & 50 & 0.0053 & 0.1542 & 0.9325 \\ 
  IRS-Model & Random & Lognormal & 0.9 & 50 & -0.0012 & 0.1160 & 0.9115 \\ 
  GRTS-Design & Random & Lognormal & 0.9 & 50 & -0.0033 & 0.1150 & 0.9160 \\ 
  GRTS-Model & Random & Lognormal & 0.9 & 50 & -0.0031 & 0.1014 & 0.9235 \\ 

@@

\caption{Approach, layout (Layout), response type (Response) roportion of dependent error (DE Prop), sample size (n), mean (prediction) bias (Bias), root-mean-squared-(prediction) error (rMS(P)E), and 95\% interval coverage (Coverage) for a simulation scenario.} 

@@

IRS-Design & Gridded & Normal & 0 & 100 & -0.0029 & 0.1322 & 0.9430 \\ 
  IRS-Model & Gridded & Normal & 0 & 100 & -0.0033 & 0.1332 & 0.9410 \\ 
  GRTS-Design & Gridded & Normal & 0 & 100 & 0.0041 & 0.1302 & 0.9245 \\ 
  GRTS-Model & Gridded & Normal & 0 & 100 & 0.0038 & 0.1304 & 0.9420 \\ 

@@

\caption{Approach, layout (Layout), response type (Response) roportion of dependent error (DE Prop), sample size (n), mean (prediction) bias (Bias), root-mean-squared-(prediction) error (rMS(P)E), and 95\% interval coverage (Coverage) for a simulation scenario.} 

@@

IRS-Design & Gridded & Lognormal & 0 & 100 & -0.0052 & 0.1334 & 0.9335 \\ 
  IRS-Model & Gridded & Lognormal & 0 & 100 & -0.0072 & 0.1350 & 0.9300 \\ 
  GRTS-Design & Gridded & Lognormal & 0 & 100 & 0.0042 & 0.1303 & 0.9035 \\ 
  GRTS-Model & Gridded & Lognormal & 0 & 100 & 0.0034 & 0.1307 & 0.9265 \\ 

@@

\caption{Approach, layout (Layout), response type (Response) roportion of dependent error (DE Prop), sample size (n), mean (prediction) bias (Bias), root-mean-squared-(prediction) error (rMS(P)E), and 95\% interval coverage (Coverage) for a simulation scenario.} 

@@

IRS-Design & Random & Normal & 0 & 100 & -0.0066 & 0.1366 & 0.9405 \\ 
  IRS-Model & Random & Normal & 0 & 100 & -0.0067 & 0.1370 & 0.9385 \\ 
  GRTS-Design & Random & Normal & 0 & 100 & 0.0028 & 0.1364 & 0.9180 \\ 
  GRTS-Model & Random & Normal & 0 & 100 & 0.0029 & 0.1363 & 0.9345 \\ 

@@

\caption{Approach, layout (Layout), response type (Response) roportion of dependent error (DE Prop), sample size (n), mean (prediction) bias (Bias), root-mean-squared-(prediction) error (rMS(P)E), and 95\% interval coverage (Coverage) for a simulation scenario.} 

@@

IRS-Design & Random & Lognormal & 0 & 100 & -0.0051 & 0.1348 & 0.9280 \\ 
  IRS-Model & Random & Lognormal & 0 & 100 & -0.0075 & 0.1372 & 0.9230 \\ 
  GRTS-Design & Random & Lognormal & 0 & 100 & 0.0002 & 0.1375 & 0.8840 \\ 
  GRTS-Model & Random & Lognormal & 0 & 100 & -0.0003 & 0.1377 & 0.9090 \\ 

@@

\caption{Approach, layout (Layout), response type (Response) roportion of dependent error (DE Prop), sample size (n), mean (prediction) bias (Bias), root-mean-squared-(prediction) error (rMS(P)E), and 95\% interval coverage (Coverage) for a simulation scenario.} 

@@

IRS-Design & Gridded & Normal & 0.5 & 100 & -0.0016 & 0.1177 & 0.9540 \\ 
  IRS-Model & Gridded & Normal & 0.5 & 100 & -0.0023 & 0.1072 & 0.9470 \\ 
  GRTS-Design & Gridded & Normal & 0.5 & 100 & 0.0051 & 0.0998 & 0.9300 \\ 
  GRTS-Model & Gridded & Normal & 0.5 & 100 & 0.0039 & 0.0982 & 0.9470 \\ 

@@

\caption{Approach, layout (Layout), response type (Response) roportion of dependent error (DE Prop), sample size (n), mean (prediction) bias (Bias), root-mean-squared-(prediction) error (rMS(P)E), and 95\% interval coverage (Coverage) for a simulation scenario.} 

@@

IRS-Design & Gridded & Lognormal & 0.5 & 100 & -0.0021 & 0.1211 & 0.9445 \\ 
  IRS-Model & Gridded & Lognormal & 0.5 & 100 & -0.0058 & 0.1153 & 0.9295 \\ 
  GRTS-Design & Gridded & Lognormal & 0.5 & 100 & 0.0041 & 0.1090 & 0.9085 \\ 
  GRTS-Model & Gridded & Lognormal & 0.5 & 100 & 0.0019 & 0.1090 & 0.9180 \\ 

@@

\caption{Approach, layout (Layout), response type (Response) roportion of dependent error (DE Prop), sample size (n), mean (prediction) bias (Bias), root-mean-squared-(prediction) error (rMS(P)E), and 95\% interval coverage (Coverage) for a simulation scenario.} 

@@

IRS-Design & Random & Normal & 0.5 & 100 & -0.0064 & 0.1222 & 0.9440 \\ 
  IRS-Model & Random & Normal & 0.5 & 100 & -0.0049 & 0.1073 & 0.9440 \\ 
  GRTS-Design & Random & Normal & 0.5 & 100 & 0.0013 & 0.1041 & 0.9155 \\ 
  GRTS-Model & Random & Normal & 0.5 & 100 & 0.0014 & 0.1020 & 0.9400 \\ 

@@

\caption{Approach, layout (Layout), response type (Response) roportion of dependent error (DE Prop), sample size (n), mean (prediction) bias (Bias), root-mean-squared-(prediction) error (rMS(P)E), and 95\% interval coverage (Coverage) for a simulation scenario.} 

@@

IRS-Design & Random & Lognormal & 0.5 & 100 & -0.0063 & 0.1204 & 0.9355 \\ 
  IRS-Model & Random & Lognormal & 0.5 & 100 & -0.0097 & 0.1150 & 0.9275 \\ 
  GRTS-Design & Random & Lognormal & 0.5 & 100 & 0.0003 & 0.1092 & 0.8960 \\ 
  GRTS-Model & Random & Lognormal & 0.5 & 100 & -0.0004 & 0.1088 & 0.9120 \\ 

@@

\caption{Approach, layout (Layout), response type (Response) roportion of dependent error (DE Prop), sample size (n), mean (prediction) bias (Bias), root-mean-squared-(prediction) error (rMS(P)E), and 95\% interval coverage (Coverage) for a simulation scenario.} 

>>>>

Recall the four sampling-analysis combinations from the simulation
study, summarized in Table \ref{tab:designanalysis}. Also recall the 36
parameter configurations from the simulation study, summarized in Table
\ref{tab:parmtab}.

\begin{table}[ht]
\centering
\begin{tabular}{r|ll}
  \hline
 & Design & Model \\ 
  \hline
IRS & IRS-Design & IRS-Model \\ 
  GRTS & GRTS-Design & GRTS-Model \\ 
   \hline
\end{tabular}
\caption{\label{tab:designanalysis} Sampling-analysis combinations in the simulation study. The rows give the two types of sampling designs and the columns give the two types of analyses.} 
\end{table}

\begin{table}[ht]
\centering
\begin{tabular}{r|lll}
   \hline
Sample Size (n) & 50 & 100 & 200 \\ 
  Layout & Random & Gridded & - \\ 
  Proportion of Dependent Error & 0 & 0.5 & 0.9 \\ 
  Response Type & Normal & Lognormal & - \\ 
   \hline
\end{tabular}
\caption{\label{tab:parmtab} Simulation scenario options. All combinations of sample size, location layout, response type, and proportion of dependent random error composed the 36 simulation scenarios. In each simualtion scenario, the total variance was 2.} 
\end{table}

Next we present tables summarizing mean estimation bias (design-based)
or mean prediction bias (model-based), mean standard errors,
root-mean-squared error (design-based) or root-mean-squared-prediction
error (model-based), and 95\% confidence interval coverage
(design-based) or 95\% prediction interval coverage (model-based) for
all 36 simulation scenarios.

@@

\scalebox{0.8}{
\begin{tabular}{lllrrrrrr}

@@

Approach & Layout & Response & PDE & n & Bias & rMS(P)E & MStdE & Coverage \\ 

@@

IRS-Design & Gridded & Normal & 0 & 50 & -0.0023 & 0.1968 & 0.1936 & 0.9440 \\ 
  IRS-Model & Gridded & Normal & 0 & 50 & -0.0029 & 0.1988 & 0.1917 & 0.9400 \\ 
  GRTS-Design & Gridded & Normal & 0 & 50 & -0.0011 & 0.1946 & 0.1703 & 0.9110 \\ 
  GRTS-Model & Gridded & Normal & 0 & 50 & -0.0006 & 0.1949 & 0.1875 & 0.9300 \\ 

@@

\caption{Sampling-analysis combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (PDE), sample size (n), mean (prediction) bias (Bias), root-mean-squared-(prediction) error (rMS(P)E), mean standard error (MStdE), and 95\% interval coverage (Coverage) in simulation scenario 1.} 

@@

IRS-Design & Gridded & Lognormal & 0 & 50 & -0.0036 & 0.2007 & 0.1855 & 0.9080 \\ 
  IRS-Model & Gridded & Lognormal & 0 & 50 & -0.0094 & 0.2071 & 0.1833 & 0.9045 \\ 
  GRTS-Design & Gridded & Lognormal & 0 & 50 & -0.0007 & 0.1962 & 0.1629 & 0.8690 \\ 
  GRTS-Model & Gridded & Lognormal & 0 & 50 & -0.0022 & 0.1969 & 0.1787 & 0.8945 \\ 

@@

\caption{Sampling-analysis combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (PDE), sample size (n), mean (prediction) bias (Bias), root-mean-squared-(prediction) error (rMS(P)E), mean standard error (MStdE), and 95\% interval coverage (Coverage) in simulation scenario 2.} 

@@

IRS-Design & Random & Normal & 0 & 50 & 0.0019 & 0.1861 & 0.1935 & 0.9505 \\ 
  IRS-Model & Random & Normal & 0 & 50 & 0.0014 & 0.1892 & 0.1912 & 0.9445 \\ 
  GRTS-Design & Random & Normal & 0 & 50 & -0.0040 & 0.1955 & 0.1709 & 0.9090 \\ 
  GRTS-Model & Random & Normal & 0 & 50 & -0.0040 & 0.1965 & 0.1879 & 0.9315 \\ 

@@

\caption{Sampling-analysis combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (PDE), sample size (n), mean (prediction) bias (Bias), root-mean-squared-(prediction) error (rMS(P)E), mean standard error (MStdE), and 95\% interval coverage (Coverage) in simulation scenario 3.} 

@@

IRS-Design & Random & Lognormal & 0 & 50 & 0.0032 & 0.1843 & 0.1833 & 0.9205 \\ 
  IRS-Model & Random & Lognormal & 0 & 50 & -0.0039 & 0.1945 & 0.1808 & 0.9105 \\ 
  GRTS-Design & Random & Lognormal & 0 & 50 & -0.0056 & 0.1944 & 0.1634 & 0.8870 \\ 
  GRTS-Model & Random & Lognormal & 0 & 50 & -0.0078 & 0.1967 & 0.1789 & 0.9075 \\ 

@@

\caption{Sampling-analysis combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (PDE), sample size (n), mean (prediction) bias (Bias), root-mean-squared-(prediction) error (rMS(P)E), mean standard error (MStdE), and 95\% interval coverage (Coverage) in simulation scenario 4.} 

@@

IRS-Design & Gridded & Normal & 0.5 & 50 & 0.0025 & 0.1762 & 0.1748 & 0.9470 \\ 
  IRS-Model & Gridded & Normal & 0.5 & 50 & 0.0007 & 0.1655 & 0.1567 & 0.9305 \\ 
  GRTS-Design & Gridded & Normal & 0.5 & 50 & 0.0004 & 0.1524 & 0.1357 & 0.9115 \\ 
  GRTS-Model & Gridded & Normal & 0.5 & 50 & -0.0003 & 0.1499 & 0.1453 & 0.9320 \\ 

@@

\caption{Sampling-analysis combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (PDE), sample size (n), mean (prediction) bias (Bias), root-mean-squared-(prediction) error (rMS(P)E), mean standard error (MStdE), and 95\% interval coverage (Coverage) in simulation scenario 5.} 

@@

IRS-Design & Gridded & Lognormal & 0.5 & 50 & 0.0004 & 0.1863 & 0.1627 & 0.9140 \\ 
  IRS-Model & Gridded & Lognormal & 0.5 & 50 & -0.0076 & 0.1834 & 0.1495 & 0.9035 \\ 
  GRTS-Design & Gridded & Lognormal & 0.5 & 50 & 0.0016 & 0.1612 & 0.1303 & 0.8810 \\ 
  GRTS-Model & Gridded & Lognormal & 0.5 & 50 & -0.0017 & 0.1606 & 0.1385 & 0.8940 \\ 

@@

\caption{Sampling-analysis combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (PDE), sample size (n), mean (prediction) bias (Bias), root-mean-squared-(prediction) error (rMS(P)E), mean standard error (MStdE), and 95\% interval coverage (Coverage) in simulation scenario 6.} 

@@

IRS-Design & Random & Normal & 0.5 & 50 & 0.0037 & 0.1657 & 0.1737 & 0.9590 \\ 
  IRS-Model & Random & Normal & 0.5 & 50 & 0.0027 & 0.1546 & 0.1559 & 0.9495 \\ 
  GRTS-Design & Random & Normal & 0.5 & 50 & -0.0034 & 0.1511 & 0.1355 & 0.9170 \\ 
  GRTS-Model & Random & Normal & 0.5 & 50 & -0.0037 & 0.1504 & 0.1447 & 0.9305 \\ 

@@

\caption{Sampling-analysis combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (PDE), sample size (n), mean (prediction) bias (Bias), root-mean-squared-(prediction) error (rMS(P)E), mean standard error (MStdE), and 95\% interval coverage (Coverage) in simulation scenario 7.} 

@@

IRS-Design & Random & Lognormal & 0.5 & 50 & 0.0023 & 0.1637 & 0.1574 & 0.9245 \\ 
  IRS-Model & Random & Lognormal & 0.5 & 50 & -0.0055 & 0.1622 & 0.1443 & 0.9125 \\ 
  GRTS-Design & Random & Lognormal & 0.5 & 50 & -0.0057 & 0.1570 & 0.1287 & 0.9000 \\ 
  GRTS-Model & Random & Lognormal & 0.5 & 50 & -0.0079 & 0.1567 & 0.1362 & 0.9100 \\ 

@@

\caption{Sampling-analysis combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (PDE), sample size (n), mean (prediction) bias (Bias), root-mean-squared-(prediction) error (rMS(P)E), mean standard error (MStdE), and 95\% interval coverage (Coverage) in simulation scenario 8.} 

@@

IRS-Design & Gridded & Normal & 0.9 & 50 & 0.0053 & 0.1579 & 0.1570 & 0.9470 \\ 
  IRS-Model & Gridded & Normal & 0.9 & 50 & 0.0026 & 0.1165 & 0.1094 & 0.9315 \\ 
  GRTS-Design & Gridded & Normal & 0.9 & 50 & 0.0013 & 0.1074 & 0.0996 & 0.9220 \\ 
  GRTS-Model & Gridded & Normal & 0.9 & 50 & -0.0007 & 0.0949 & 0.0938 & 0.9430 \\ 

@@

\caption{Sampling-analysis combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (PDE), sample size (n), mean (prediction) bias (Bias), root-mean-squared-(prediction) error (rMS(P)E), mean standard error (MStdE), and 95\% interval coverage (Coverage) in simulation scenario 9.} 

@@

IRS-Design & Gridded & Lognormal & 0.9 & 50 & 0.0031 & 0.1731 & 0.1412 & 0.9220 \\ 
  IRS-Model & Gridded & Lognormal & 0.9 & 50 & -0.0020 & 0.1325 & 0.1051 & 0.9135 \\ 
  GRTS-Design & Gridded & Lognormal & 0.9 & 50 & 0.0031 & 0.1183 & 0.0954 & 0.9065 \\ 
  GRTS-Model & Gridded & Lognormal & 0.9 & 50 & -0.0002 & 0.1090 & 0.0909 & 0.9120 \\ 

@@

\caption{Sampling-analysis combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (PDE), sample size (n), mean (prediction) bias (Bias), root-mean-squared-(prediction) error (rMS(P)E), mean standard error (MStdE), and 95\% interval coverage (Coverage) in simulation scenario 10.} 

@@

IRS-Design & Random & Normal & 0.9 & 50 & 0.0062 & 0.1520 & 0.1545 & 0.9525 \\ 
  IRS-Model & Random & Normal & 0.9 & 50 & 0.0037 & 0.1074 & 0.1078 & 0.9525 \\ 
  GRTS-Design & Random & Normal & 0.9 & 50 & -0.0029 & 0.1038 & 0.0984 & 0.9340 \\ 
  GRTS-Model & Random & Normal & 0.9 & 50 & -0.0027 & 0.0940 & 0.0921 & 0.9360 \\ 

@@

\caption{Sampling-analysis combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (PDE), sample size (n), mean (prediction) bias (Bias), root-mean-squared-(prediction) error (rMS(P)E), mean standard error (MStdE), and 95\% interval coverage (Coverage) in simulation scenario 11.} 

@@

IRS-Design & Random & Lognormal & 0.9 & 50 & 0.0053 & 0.1542 & 0.1351 & 0.9325 \\ 
  IRS-Model & Random & Lognormal & 0.9 & 50 & -0.0012 & 0.1160 & 0.0997 & 0.9115 \\ 
  GRTS-Design & Random & Lognormal & 0.9 & 50 & -0.0033 & 0.1150 & 0.0923 & 0.9160 \\ 
  GRTS-Model & Random & Lognormal & 0.9 & 50 & -0.0031 & 0.1014 & 0.0872 & 0.9235 \\ 

@@

\caption{Sampling-analysis combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (PDE), sample size (n), mean (prediction) bias (Bias), root-mean-squared-(prediction) error (rMS(P)E), mean standard error (MStdE), and 95\% interval coverage (Coverage) in simulation scenario 12.} 

@@

IRS-Design & Gridded & Normal & 0 & 100 & -0.0029 & 0.1322 & 0.1333 & 0.9430 \\ 
  IRS-Model & Gridded & Normal & 0 & 100 & -0.0033 & 0.1332 & 0.1326 & 0.9410 \\ 
  GRTS-Design & Gridded & Normal & 0 & 100 & 0.0041 & 0.1302 & 0.1208 & 0.9245 \\ 
  GRTS-Model & Gridded & Normal & 0 & 100 & 0.0038 & 0.1304 & 0.1309 & 0.9420 \\ 

@@

\caption{Sampling-analysis combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (PDE), sample size (n), mean (prediction) bias (Bias), root-mean-squared-(prediction) error (rMS(P)E), mean standard error (MStdE), and 95\% interval coverage (Coverage) in simulation scenario 13.} 

@@

IRS-Design & Gridded & Lognormal & 0 & 100 & -0.0052 & 0.1334 & 0.1309 & 0.9335 \\ 
  IRS-Model & Gridded & Lognormal & 0 & 100 & -0.0072 & 0.1350 & 0.1301 & 0.9300 \\ 
  GRTS-Design & Gridded & Lognormal & 0 & 100 & 0.0042 & 0.1303 & 0.1170 & 0.9035 \\ 
  GRTS-Model & Gridded & Lognormal & 0 & 100 & 0.0034 & 0.1307 & 0.1266 & 0.9265 \\ 

@@

\caption{Sampling-analysis combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (PDE), sample size (n), mean (prediction) bias (Bias), root-mean-squared-(prediction) error (rMS(P)E), mean standard error (MStdE), and 95\% interval coverage (Coverage) in simulation scenario 14.} 

@@

IRS-Design & Random & Normal & 0 & 100 & -0.0066 & 0.1366 & 0.1329 & 0.9405 \\ 
  IRS-Model & Random & Normal & 0 & 100 & -0.0067 & 0.1370 & 0.1322 & 0.9385 \\ 
  GRTS-Design & Random & Normal & 0 & 100 & 0.0028 & 0.1364 & 0.1210 & 0.9180 \\ 
  GRTS-Model & Random & Normal & 0 & 100 & 0.0029 & 0.1363 & 0.1310 & 0.9345 \\ 

@@

\caption{Sampling-analysis combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (PDE), sample size (n), mean (prediction) bias (Bias), root-mean-squared-(prediction) error (rMS(P)E), mean standard error (MStdE), and 95\% interval coverage (Coverage) in simulation scenario 15.} 

@@

IRS-Design & Random & Lognormal & 0 & 100 & -0.0051 & 0.1348 & 0.1298 & 0.9280 \\ 
  IRS-Model & Random & Lognormal & 0 & 100 & -0.0075 & 0.1372 & 0.1290 & 0.9230 \\ 
  GRTS-Design & Random & Lognormal & 0 & 100 & 0.0002 & 0.1375 & 0.1181 & 0.8840 \\ 
  GRTS-Model & Random & Lognormal & 0 & 100 & -0.0003 & 0.1377 & 0.1275 & 0.9090 \\ 

@@

\caption{Sampling-analysis combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (PDE), sample size (n), mean (prediction) bias (Bias), root-mean-squared-(prediction) error (rMS(P)E), mean standard error (MStdE), and 95\% interval coverage (Coverage) in simulation scenario 16.} 

@@

IRS-Design & Gridded & Normal & 0.5 & 100 & -0.0016 & 0.1177 & 0.1201 & 0.9540 \\ 
  IRS-Model & Gridded & Normal & 0.5 & 100 & -0.0023 & 0.1072 & 0.1057 & 0.9470 \\ 
  GRTS-Design & Gridded & Normal & 0.5 & 100 & 0.0051 & 0.0998 & 0.0935 & 0.9300 \\ 
  GRTS-Model & Gridded & Normal & 0.5 & 100 & 0.0039 & 0.0982 & 0.0990 & 0.9470 \\ 

@@

\caption{Sampling-analysis combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (PDE), sample size (n), mean (prediction) bias (Bias), root-mean-squared-(prediction) error (rMS(P)E), mean standard error (MStdE), and 95\% interval coverage (Coverage) in simulation scenario 17.} 

@@

IRS-Design & Gridded & Lognormal & 0.5 & 100 & -0.0021 & 0.1211 & 0.1137 & 0.9445 \\ 
  IRS-Model & Gridded & Lognormal & 0.5 & 100 & -0.0058 & 0.1153 & 0.1032 & 0.9295 \\ 
  GRTS-Design & Gridded & Lognormal & 0.5 & 100 & 0.0041 & 0.1090 & 0.0910 & 0.9085 \\ 
  GRTS-Model & Gridded & Lognormal & 0.5 & 100 & 0.0019 & 0.1090 & 0.0959 & 0.9180 \\ 

@@

\caption{Sampling-analysis combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (PDE), sample size (n), mean (prediction) bias (Bias), root-mean-squared-(prediction) error (rMS(P)E), mean standard error (MStdE), and 95\% interval coverage (Coverage) in simulation scenario 18.} 

@@

IRS-Design & Random & Normal & 0.5 & 100 & -0.0064 & 0.1222 & 0.1190 & 0.9440 \\ 
  IRS-Model & Random & Normal & 0.5 & 100 & -0.0049 & 0.1073 & 0.1051 & 0.9440 \\ 
  GRTS-Design & Random & Normal & 0.5 & 100 & 0.0013 & 0.1041 & 0.0932 & 0.9155 \\ 
  GRTS-Model & Random & Normal & 0.5 & 100 & 0.0014 & 0.1020 & 0.0986 & 0.9400 \\ 

@@

\caption{Sampling-analysis combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (PDE), sample size (n), mean (prediction) bias (Bias), root-mean-squared-(prediction) error (rMS(P)E), mean standard error (MStdE), and 95\% interval coverage (Coverage) in simulation scenario 19.} 

@@

IRS-Design & Random & Lognormal & 0.5 & 100 & -0.0063 & 0.1204 & 0.1108 & 0.9355 \\ 
  IRS-Model & Random & Lognormal & 0.5 & 100 & -0.0097 & 0.1150 & 0.1005 & 0.9275 \\ 
  GRTS-Design & Random & Lognormal & 0.5 & 100 & 0.0003 & 0.1092 & 0.0891 & 0.8960 \\ 
  GRTS-Model & Random & Lognormal & 0.5 & 100 & -0.0004 & 0.1088 & 0.0937 & 0.9120 \\ 

@@

\caption{Sampling-analysis combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (PDE), sample size (n), mean (prediction) bias (Bias), root-mean-squared-(prediction) error (rMS(P)E), mean standard error (MStdE), and 95\% interval coverage (Coverage) in simulation scenario 20.} 
